Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2021-03-10 reviews/response.tex

\documentclass[11pt]{article}
\usepackage{fullpage,amsfonts,amsmath}

\title{Response to the reviews of the manuscript: ``Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference'' by Zheng Gao
and Stilian Stoev submitted to {\em SpringerBriefs Series in Probability and Statistics} }

\begin{document}
 \maketitle

 \section*{Summary of the revision}

 We sincerely thank the managing Editor and the five anonymous referees for their very helpful and constructive suggestions.  We really 
 appreciate the reviewers' time, effort, and thoughtful suggestions, which stimulated us to substantially revise and improve the manuscript.
 We begin with a high-level description of our edits and in the following section we respond to specific points raised by the reviewers.

 \begin{itemize}
  \item {\bf (Summary)} The revised manuscript has now a brief introductory chapter and 6 substantive chapters, 
  which amount to a total of 124 pages. As with the original submission,  Chapter 2 reviews the statistical risks, estimation and testing procedures,
  as well as probability models for the errors used in the rest of the manuscript.  It contains also a high-level summary of our results 
  in the context of the existing literature and some auxiliary facts from probability and extreme value theory.  For convenience of the reader, we 
  have added statements of Slepyan's Lemma and the Sudakov-Fernique inequality (without proofs).

   Chapter 3 provides a panorama of the phase-transition results in the signal detection and support estimation problems for the
   iid Gaussian error model.  Its purpose is to emphasize ideas and provide an accessible account, including references to the state-of-the-art 
   in the literature.  The chapter contains also some new results on the (sub)optimality of some popular statistics, which appear to have been 
   overlooked in the literature (Theorem 3.1).  One main idea  behind the exposition is to systematically present the different types of phase transition 
   results as a function of the chosen statistical risk.

   Chapters 4 through 7 contain the core of our contributions.

   Chapter 4 establishes phase-transitions results for the exact support recovery problem in the additive error model.  The main themes of this 
   chapter are {\em error--dependence} and {\em concentration of maxima}. We establish that the notion of uniform relative stability -- 
   a type of concentration of maxima phenomenon -- is key to characterizing the phase-transition in exact support recovery for the general class 
   of thresholding estimators.

   Chapter 5 begins with a study of the finite-sample (Bayes) optimality and sub-optimality of the threshold-based support estimators.  
   Criteria for the latter are established and certain theoretical results indicate that likelihood thresholding is in general optimal, when the thresholding 
   estimators are sub-optimal.  In the regime when the thresholding estimators are optimal, i.e., for log-concave error densities, our results entail 
   a universal statistical limit for exact support recovery, valid over all estimators (Theorem 5.1).   On the other hand, for the general class of
   thresholding estimators, we obtain minimax characterizations of the phase-transition in exact support recovery, for every fixed error-dependence 
   structure that satisfies mild uniform relative stability condition (Corollary 5.2).

   These finite-sample optimality results are used to obtain a variety of asymptotic minimax optimality results.  Consequently,

    for the large class of
   thresholding estimators. For example, the phase-transition in exact support recovery is shown to  universal among all estimators and  result is obtained for the minimax optimal exact support estimators under 
   log-concave error distributions (

   Under independent 
   errors, criteria for the 
   that the errors can

   We have revised substantially Chapters 4 and 5.

  \item {\bf (Organization)} Following a suggestion of a reviewer ({\bf R2}),  we have included most proofs 
  in the text right after the corresponding claims (theorems, propositions, lemmas).  In the interest of space and to conform with the format of
  the SpringerBriefs series, we no longer include ``Exercise'' sections.

  Last but not least, to better balance the exposition, we decided to divide the previous
  Chapter 4 into two new chapters (now Ch.\ 4, entitled ``Exact Support Recovery Under Dependence'', 
  and Ch.\ 5 ``Bayes and Minimax Optimality'').  In addition to making all chapters more manageable and of about equal length, it exposes more
  clearly our contributions.  The results contained in Chapters 4 and 5 as well as the more probabilistic Chapter 6 and more applied Chapter 7 are 
  original and new contributions to the literature.

 \end{itemize}

 \section*{Responses to specific points raised by the reviewers}
\end{document}

### 2021-03-10 5.Bayes.optimality/5.Bayes_optimality_and_minimax.tex
Ch 5
Upgraded fromer Prop 5.1 & 5.3 to Thm 5.1 & 5.2, Prop 5.2 became Cor 5.1.

These are THEOREMS!

\begin{proposition} \label{prop:optimal-oracle-procedures}
Let the observations $x(i)$, $i=1,\ldots,p$ be as prescribed as in \eqref{eq:signal-distributions-ordered} through \eqref{eq:uniform-ordered}.
If each of the pairs $\{f_0, f_{1}\},\ldots,\{f_0,f_{s}\}$ forms an MLR family, then every oracle data thresholding procedure $\widehat{S}^*$ is finite-sample optimal in terms of Bayes risk $\E_\pi \P[\widehat{S} \neq S]$. That is,
\begin{equation} \label{eq:finite-sample-Bayes-optimal}
    \widehat{S}^* \in \argmin_{\widehat{S}} \E_\pi \P[\widehat{S} \neq S].
\end{equation}
for all $s$ and $p$.
\end{proposition} 
\begin{proof}%[Proof of Proposition \ref{prop:optimal-oracle-procedures}]
The problem of support recovery can be equivalently stated as a classification problem, where the discrete parameter space is $\mathcal{S} = \{S\subseteq\{1,\ldots,p\}:|S|=s\}$, and the observation $x \in\R^p$ has likelihood $f(x|S)$ indexed by the support set $S$.

@@

We emphasize that under the MLR conditions in Proposition \ref{prop:optimal-oracle-procedures},
 the oracle thresholding procedures are in fact \emph{finite-sample optimal} in the 
above Bayesian context. Further, our setup allows for different alternative distributions, and relaxes the assumptions 
of \citet{butucea2018variable} when studying distributional generalizations, where the alternatives are assumed to be identically distributed.

It remains to understand when the key MLR property holds.  We elaborate on this question next.
Returning to the more concrete signal-plus-noise model \eqref{eq:model-additive}, it turns out that the error tail behavior is what determines the optimality of data thresholding procedures.
In this setting, log-concavity of the error densities is \emph{equivalent} to the MLR property (Lemma \ref{lemma:MLR-log-concavity}). This, in turn, yields the finite-sample optimality of data thresholding procedures (Proposition \ref{prop:log-concave}).

@@

Proposition \ref{prop:optimal-oracle-procedures} and Lemma \ref{lemma:MLR-log-concavity} yield immediately the following.

\begin{proposition} \label{prop:log-concave}
Consider the additive error model \eqref{eq:model-additive}, where the $\epsilon(i)$'s are
independent with common distribution $F$.  Let the signal $\mu$ have $s$ positive entries with magnitudes $0<\delta_1\le\ldots\le\delta_s$, located on $\{1,\ldots,p\}$ as prescribed in \eqref{eq:uniform-ordered}.

If $F$ has a positive, log-concave density $f$, then the support estimator % oracle thresholding procedure 
$$
 \widehat{S}^* := \{i\, :\, x(i)\ge x_{[s]}\}
$$ 
is  %a.s.\ unique and
finite-sample optimal in terms of Bayes risk in the sense of \eqref{eq:finite-sample-Bayes-optimal}.
\end{proposition} 
\begin{proof} The independence and the fact that the observations have densities implies the absence of 
ties among the order statistics $\{x_{[i]}\}$, with probability one.  Thus, the oracle thresholding procedure is a.s.\ unique 
and given by $\widehat{S}^* = \{i\, :\, x(i)\ge x_{[s]}\}$.  The result then follows from 
Proposition \ref{prop:optimal-oracle-procedures} and Lemma \ref{lemma:MLR-log-concavity}.
\end{proof}

\begin{remark}
Propositions \ref{prop:optimal-oracle-procedures} and \ref{prop:log-concave} show that under MLR (or equivalently, 
log-concavity of the errors in additive models), the oracle thresholding procedures are finite-sample optimal even in the case where the signals have different (positive) sizes. This fascinating property perhaps 
explains the success of the thresholding estimators.
\end{remark}

@@

\begin{example} \label{exmp:AGG-logconcave}
The generalized Gaussian density $f(x)\propto \exp\{-|x|^\nu/\nu\}$ is log-concave for all $\nu\ge1$.
Therefore in the additive error model \eqref{eq:model-additive}, according to Proposition \ref{prop:log-concave}, the oracle thresholding procedure is Bayes optimal in the sense of \eqref{eq:finite-sample-Bayes-optimal}.
\end{example}

@@

When the MLR condition in Proposition \ref{prop:optimal-oracle-procedures} is violated, the oracle thresholding 
procedures can in fact be sub-optimal (see Example \ref{exmp:suboptimal-data-thresholding} and 
Section \ref{sec:sup-optimality-of-thresholding}, below).  
%

@@

\begin{definition}[Oracle likelihood ratio thresholding] Recall that $\langle a_1,\cdots,a_s\rangle$ denotes
the vector of $a_i$'s arranged in a non-increasing order.  Any estimator $\hat S = \{i_1,\cdots,i_s\}$ such that
$$
\langle L(i_1),\cdots,L(i_s) \rangle = (L_{[1]},\cdots,L_{[s]}),
$$
will be referred to as an {\em oracle likelihood thresholding} estimator of the support $S$.
\end{definition}
\begin{proposition} \label{prop:likelihood-ratio-thresholding} Any oracle likelihood ratio thresholding 
procedure $\widehat{S}_{\text{LRT}}$ is finite-sample optimal in terms of Bayes risk. That is,
\begin{equation}
    \widehat{S}_{\text{LRT}} \in \argmin_{\widehat{S} \in {\mathcal S}} \E_\pi \P[\widehat{S} \neq S].
\end{equation}
for all $s$ and $p$, where the infimum on $\widehat{S}$ is taken over all support estimators of size $s$.
\end{proposition}

\begin{proof}%[Proof of Proposition \ref{prop:likelihood-ratio-thresholding}]
The proof is analogous to that of Proposition \ref{prop:optimal-oracle-procedures}.
We need to show that
$
\widehat{S}_{\rm LRT} \in \argmax_{S \in \mathcal{S}} f(x|S) \pi(S).
$
Since the distribution $\pi$ of the support $S$ 
is uniform (recall \eqref{eq:uniform}), it is equivalent to prove that 
$$
f(x|\widehat{S}_{\text{LRT}}) = \max_{S \in \mathcal {S}} f(x|S),
$$ 
where  $f(x|S)$ is the conditional distribution of the data given the unordered support $S$,
\begin{equation} \label{eq:likelihood-ratio-thresholding-proof}
    f(x|S) = \sum_P f(x|P) \pi^{\text{ord}}(P|S) = \prod_{j\in S} f_a(x(j)) \prod_{j\not\in S}{f_0(x(j))}.
\end{equation}
Suppose $\widehat S\in {\mathcal S}$ is {\em not} an oracle likelihood thresholding estimator. 
Then from the definition of the likelihood ratio thresholding procedure, there 
must be indices 
$j \in \widehat S$ and $j' \not \in \widehat{S}$ such that $L(j) < L(j')$.
If we exchange the labels of $L(j)$ and $L(j')$, that is, we form a new estimate 
$\widehat{S}\,' = \big(\widehat{S}\setminus\{j\}\big)\cup\{j'\}$,
comparing the log-likelihoods under $\widehat{S}$ and $\widehat{S}\,'$, we have
\begin{equation*}
    \log{f(x|\widehat{S})} - \log{f(x|\widehat{S}\,')} 
    = \log{f_a(x(j))} + \log{f_0(x(j'))} - \log{f_a(x(j'))} - \log{f_0(x(j))}.
\end{equation*}
By the definition of $L(j)$'s, and the order relations, we obtain
\begin{equation*}
    \log{f(x|\widehat{S})} - \log{f(x|\widehat{S}\,')} 
    = \log{L(j)} - \log{L(j')} > 0
\end{equation*}
This shows that $\widehat S$ cannot be Bayes optimal unless it is a likelihood thresholding estimator.
Note that with the same argument for every two likelihood thresholding estimators $\widehat S'$
and $\widehat S''$, we have $ f(x|\widehat{S}') = f(x|\widehat{S}'')$, proving the desired optimality.
\end{proof}

The characterization of optimal likelihood ratio thresholding procedures in Proposition \ref{prop:likelihood-ratio-thresholding} may not always yield practical estimators, as the density of the alternatives, and the number of signals $s$ 
are typically unknown. Still, some insights can be gained by virtue of Proposition \ref{prop:likelihood-ratio-thresholding}.
In particular, when MLR fails (for example, when the errors in model \eqref{eq:model-additive} do not have log-concave densities), data thresholding is sub-optimal.

@@

\begin{proof}[Corollary \ref{cor:log-convex}]
Since the density of the alternatives $f_{a}(t) = {f(t-\delta)}$ is log-convex on $[K+\delta, \infty)$, by Relation \eqref{eq:concavity-implies-MLR} in the proof of Lemma \ref{lemma:MLR-log-concavity} and appealing to log-convexity (rather than log-concavity), the likelihood ratio
$$
L(j) := \frac{f_a(x(j))}{f_0(x(j))} %= \sum_{i=1}^s \frac{p_if_{i}(x(j))}{f_0(x(j))},
$$
is decreasing in $x(j)$ on $[K+\delta, \infty)$.  The claim follows from Proposition \ref{prop:likelihood-ratio-thresholding}.
\end{proof}

\begin{remark}[{\bf An open problem\!}\,] As we have seen, the thresholding estimators are no longer optimal 
in the additive model with error-densities heavier than exponential.   Thanks to Proposition 
\ref{prop:likelihood-ratio-thresholding}, the oracle likelihood thresholding procedures are promising alternatives
that can lead us to practical support estimators.

In the case where the signals have different sizes, however, the argument in the proof of Proposition \ref{prop:likelihood-ratio-thresholding} breaks downs since the signal densities need to be identical for Relation \eqref{eq:likelihood-ratio-thresholding-proof} to hold.  In such cases, the characterization of the optimal procedure is an open problem.
\end{remark}

@@

Consider the asymptotic Bayes risk as defined in \eqref{eq:Bayes-risk}. The statement for the 
necessary condition of support recovery in Theorem \ref{thm:necessary}, with the help of Proposition 
\ref{prop:log-concave}, can be strengthened to include all procedures (in the Bayesian context), regardless 
of whether they are thresholding or not.

\begin{theorem} \label{thm:necessary-strengthened}
Consider the additive model \eqref{eq:model-additive} where the $\epsilon_p(i)$'s are independent and identically distributed with log-concave densities in the AGG class. 
Let the signals be as prescribed in Proposition \ref{prop:log-concave}.
If the signal sizes fall below the strong classification boundary \eqref{eq:strong-classification-boundary}, 
i.e. $\overline{r}<g(\beta)$, then we have
\begin{equation} \label{eq:classification-impossible-Bayes}
    \liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_\pi \P[\widehat{S}_p\neq S_p] = 1,
\end{equation}
where the infimum on $\widehat{S}_p$ is taken over all procedures.
\end{theorem}

\begin{proof}%[Proof of Theorem \ref{thm:necessary-strengthened}]
When the errors are independent with log-concave density, the oracle thresholding procedure $\widehat{S}^*_p$, by Proposition \ref{prop:log-concave}, minimizes the Bayes risk \eqref{eq:Bayes-risk} among \emph{all} procedures. That is,
$$
\liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_\pi\P[\widehat{S}_p\neq S_p]
\ge \liminf_{p\to\infty} \E_\pi\P[\widehat{S}^*_p\neq S_p].
$$
Since $\widehat{S}^*_p$ belongs to the class of all thresholding procedures, we have
\begin{align*}
    \liminf_{p\to\infty} \E_\pi\P[\widehat{S}^*_p\neq S_p] 
    &\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \E_\pi\P[\widehat{S}_p\neq S_p] \\
    &\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \inf_{S_p} \P[\widehat{S}_p\neq S_p] = 1,
\end{align*}
when $\overline{r}<g(\beta)$, where the last line follows from Theorem \ref{thm:necessary}.
\end{proof}

@@

Theorem \ref{thm:necessary-strengthened} and Corollary \ref{cor:minimax-over-dependence} provide a nearly complete picture of the difficulty 
in the exact support  recovery problem, in the regime when the thresholding estimators are optimal. Specifically, in such cases the signal classification boundary is universal.  On the other hand, Proposition \ref{prop:likelihood-ratio-thresholding}, and indeed, Example \ref{exmp:suboptimal-data-thresholding} demonstrate that thresholding procedures are \emph{sub-optimal} for $\text{AGG}(\nu)$ models with $\nu<1$. Therefore, the optimality of thresholding
procedures (specifically, Bonferroni's procedure) only applies to $\text{AGG}(\nu)$ models with $\nu\ge1$. 
% This suggests that the condition $\nu\ge1$ in Corollary \ref{cor:minimax-over-dependence} is tight.

>>>>

\begin{theorem} \label{thm:optimal-oracle-procedures}
Let the observations $x(i)$, $i=1,\ldots,p$ be as prescribed as in \eqref{eq:signal-distributions-ordered} through \eqref{eq:uniform-ordered}.
If each of the pairs $\{f_0, f_{1}\},\ldots,\{f_0,f_{s}\}$ forms an MLR family, then every oracle data thresholding procedure $\widehat{S}^*$ is finite-sample optimal in terms of Bayes risk $\E_\pi \P[\widehat{S} \neq S]$. That is,
\begin{equation} \label{eq:finite-sample-Bayes-optimal}
    \widehat{S}^* \in \argmin_{\widehat{S}} \E_\pi \P[\widehat{S} \neq S].
\end{equation}
for all $s$ and $p$.
\end{theorem} 
\begin{proof}%[Proof of Proposition \ref{thm:optimal-oracle-procedures}]
The problem of support recovery can be equivalently stated as a classification problem, where the discrete parameter space is $\mathcal{S} = \{S\subseteq\{1,\ldots,p\}:|S|=s\}$, and the observation $x \in\R^p$ has likelihood $f(x|S)$ indexed by the support set $S$.

@@

We emphasize that under the MLR conditions in Theorem \ref{thm:optimal-oracle-procedures},
 the oracle thresholding procedures are in fact \emph{finite-sample optimal} in the 
above Bayesian context. Further, our setup allows for different alternative distributions, and relaxes the assumptions 
of \citet{butucea2018variable} when studying distributional generalizations, where the alternatives are assumed to be identically distributed.

It remains to understand when the key MLR property holds.  We elaborate on this question next.
Returning to the more concrete signal-plus-noise model \eqref{eq:model-additive}, it turns out that the error tail behavior is what determines the optimality of data thresholding procedures.
In this setting, log-concavity of the error densities is \emph{equivalent} to the MLR property (Lemma \ref{lemma:MLR-log-concavity}). This, in turn, yields the finite-sample optimality of data thresholding procedures (Theorem \ref{c:log-concave}).

@@

Theorem \ref{thm:optimal-oracle-procedures} and Lemma \ref{lemma:MLR-log-concavity} yield immediately the following.

\begin{corollary} \label{c:log-concave}
Consider the additive error model \eqref{eq:model-additive}, where the $\epsilon(i)$'s are
independent with common distribution $F$.  Let the signal $\mu$ have $s$ positive entries with magnitudes $0<\delta_1\le\ldots\le\delta_s$, located on $\{1,\ldots,p\}$ as prescribed in \eqref{eq:uniform-ordered}.

If $F$ has a positive, log-concave density $f$, then the support estimator % oracle thresholding procedure 
$$
 \widehat{S}^* := \{i\, :\, x(i)\ge x_{[s]}\}
$$ 
is  %a.s.\ unique and
finite-sample optimal in terms of Bayes risk in the sense of \eqref{eq:finite-sample-Bayes-optimal}.
\end{corollary} 
\begin{proof} The independence and the fact that the observations have densities implies the absence of 
ties among the order statistics $\{x_{[i]}\}$, with probability one.  Thus, the oracle thresholding procedure is a.s.\ unique 
and given by $\widehat{S}^* = \{i\, :\, x(i)\ge x_{[s]}\}$.  The result then follows from 
Theorem \ref{thm:optimal-oracle-procedures} and Lemma \ref{lemma:MLR-log-concavity}.
\end{proof}

\begin{remark}
Theorem \ref{thm:optimal-oracle-procedures} and Corollary \ref{c:log-concave} show that under MLR (or equivalently, 
log-concavity of the errors in additive models), the oracle thresholding procedures are finite-sample optimal even in the case where the signals have different (positive) sizes. This fascinating property perhaps 
explains the success of the thresholding estimators.
\end{remark}

@@

\begin{example} \label{exmp:AGG-logconcave}
The generalized Gaussian density $f(x)\propto \exp\{-|x|^\nu/\nu\}$ is log-concave for all $\nu\ge1$.
Therefore in the additive error model \eqref{eq:model-additive}, according to Corollary \ref{c:log-concave}, the oracle thresholding procedure is Bayes optimal in the sense of \eqref{eq:finite-sample-Bayes-optimal}.
\end{example}

@@

When the MLR condition in Theorem \ref{thm:optimal-oracle-procedures} is violated, the oracle thresholding 
procedures can in fact be sub-optimal (see Example \ref{exmp:suboptimal-data-thresholding} and 
Section \ref{sec:sup-optimality-of-thresholding}, below).  
%

@@

\begin{definition}[Oracle likelihood ratio thresholding] Recall that $\langle a_1,\cdots,a_s\rangle$ denotes
the vector of $a_i$'s arranged in a non-increasing order.  Any estimator $\hat S = \{i_1,\cdots,i_s\}$ such that
$$
\langle L(i_1),\cdots,L(i_s) \rangle = (L_{[1]},\cdots,L_{[s]}),
$$
will be referred to as an {\em oracle likelihood thresholding} estimator of the support $S$.
\end{definition}
\begin{theorem} \label{thm:likelihood-ratio-thresholding} Any oracle likelihood ratio thresholding 
procedure $\widehat{S}_{\text{LRT}}$ is finite-sample optimal in terms of Bayes risk. That is,
\begin{equation}
    \widehat{S}_{\text{LRT}} \in \argmin_{\widehat{S} \in {\mathcal S}} \E_\pi \P[\widehat{S} \neq S].
\end{equation}
for all $s$ and $p$, where the infimum on $\widehat{S}$ is taken over all support estimators of size $s$.
\end{theorem}

\begin{proof}%[Proof of Proposition \ref{thm:likelihood-ratio-thresholding}]
The proof is analogous to that of Theorem \ref{thm:optimal-oracle-procedures}.
We need to show that
$
\widehat{S}_{\rm LRT} \in \argmax_{S \in \mathcal{S}} f(x|S) \pi(S).
$
Since the distribution $\pi$ of the support $S$ 
is uniform (recall \eqref{eq:uniform}), it is equivalent to prove that 
$$
f(x|\widehat{S}_{\text{LRT}}) = \max_{S \in \mathcal {S}} f(x|S),
$$ 
where  $f(x|S)$ is the conditional distribution of the data given the unordered support $S$,
\begin{equation} \label{eq:likelihood-ratio-thresholding-proof}
    f(x|S) = \sum_P f(x|P) \pi^{\text{ord}}(P|S) = \prod_{j\in S} f_a(x(j)) \prod_{j\not\in S}{f_0(x(j))}.
\end{equation}
Suppose $\widehat S\in {\mathcal S}$ is {\em not} an oracle likelihood thresholding estimator. 
Then from the definition of the likelihood ratio thresholding procedure, there 
must be indices 
$j \in \widehat S$ and $j' \not \in \widehat{S}$ such that $L(j) < L(j')$.
If we exchange the labels of $L(j)$ and $L(j')$, that is, we form a new estimate 
$\widehat{S}\,' = \big(\widehat{S}\setminus\{j\}\big)\cup\{j'\}$,
comparing the log-likelihoods under $\widehat{S}$ and $\widehat{S}\,'$, we have
\begin{equation*}
    \log{f(x|\widehat{S})} - \log{f(x|\widehat{S}\,')} 
    = \log{f_a(x(j))} + \log{f_0(x(j'))} - \log{f_a(x(j'))} - \log{f_0(x(j))}.
\end{equation*}
By the definition of $L(j)$'s, and the order relations, we obtain
\begin{equation*}
    \log{f(x|\widehat{S})} - \log{f(x|\widehat{S}\,')} 
    = \log{L(j)} - \log{L(j')} > 0
\end{equation*}
This shows that $\widehat S$ cannot be Bayes optimal unless it is a likelihood thresholding estimator.
Note that with the same argument for every two likelihood thresholding estimators $\widehat S'$
and $\widehat S''$, we have $ f(x|\widehat{S}') = f(x|\widehat{S}'')$, proving the desired optimality.
\end{proof}

The characterization of optimal likelihood ratio thresholding procedures in Theorem \ref{thm:likelihood-ratio-thresholding} may not always yield practical estimators, as the density of the alternatives, and the number of signals $s$ 
are typically unknown. Still, some insights can be gained by virtue of Theorem \ref{thm:likelihood-ratio-thresholding}.
In particular, when MLR fails (for example, when the errors in model \eqref{eq:model-additive} do not have log-concave densities), 
data thresholding is sub-optimal.

@@

\begin{proof}[Corollary \ref{cor:log-convex}]
Since the density of the alternatives $f_{a}(t) = {f(t-\delta)}$ is log-convex on $[K+\delta, \infty)$, by Relation \eqref{eq:concavity-implies-MLR} in the proof of Lemma \ref{lemma:MLR-log-concavity} and appealing to log-convexity (rather than log-concavity), the likelihood ratio
$$
L(j) := \frac{f_a(x(j))}{f_0(x(j))} %= \sum_{i=1}^s \frac{p_if_{i}(x(j))}{f_0(x(j))},
$$
is decreasing in $x(j)$ on $[K+\delta, \infty)$.  The claim follows from Theorem \ref{thm:likelihood-ratio-thresholding}.
\end{proof}

\begin{remark}[{\bf An open problem\!}\,] As we have seen, the thresholding estimators are no longer optimal 
in the additive model with error-densities heavier than exponential.   Thanks to Theorem 
\ref{thm:likelihood-ratio-thresholding}, the oracle likelihood thresholding procedures are promising alternatives
that can lead us to practical support estimators.

In the case where the signals have different sizes, however, the argument in the proof of Theorem \ref{thm:likelihood-ratio-thresholding} breaks downs since the signal densities need to be identical for Relation \eqref{eq:likelihood-ratio-thresholding-proof} to hold.  In such cases, the characterization of the optimal procedure is an open problem.
\end{remark}

@@

Consider the asymptotic Bayes risk as defined in \eqref{eq:Bayes-risk}. The statement for the 
necessary condition of support recovery in Theorem \ref{thm:necessary}, with the help of Corollary 
\ref{c:log-concave}, can be strengthened to include all procedures (in the Bayesian context), regardless 
of whether they are thresholding or not.

\begin{theorem} \label{thm:necessary-strengthened}
Consider the additive model \eqref{eq:model-additive} where the $\epsilon_p(i)$'s are independent and identically distributed with log-concave densities in the AGG class. 
Let the signals be as prescribed in Corollary \ref{c:log-concave}.
If the signal sizes fall below the strong classification boundary \eqref{eq:strong-classification-boundary}, 
i.e. $\overline{r}<g(\beta)$, then we have
\begin{equation} \label{eq:classification-impossible-Bayes}
    \liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_\pi \P[\widehat{S}_p\neq S_p] = 1,
\end{equation}
where the infimum on $\widehat{S}_p$ is taken over all procedures.
\end{theorem}

\begin{proof}%[Proof of Theorem \ref{thm:necessary-strengthened}]
When the errors are independent with log-concave density, the oracle thresholding procedure $\widehat{S}^*_p$, by Corollary \ref{c:log-concave}, minimizes the Bayes risk \eqref{eq:Bayes-risk} among \emph{all} procedures. That is,
$$
\liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_\pi\P[\widehat{S}_p\neq S_p]
\ge \liminf_{p\to\infty} \E_\pi\P[\widehat{S}^*_p\neq S_p].
$$
Since $\widehat{S}^*_p$ belongs to the class of all thresholding procedures, we have
\begin{align*}
    \liminf_{p\to\infty} \E_\pi\P[\widehat{S}^*_p\neq S_p] 
    &\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \E_\pi\P[\widehat{S}_p\neq S_p] \\
    &\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p\in{\cal T}} \inf_{S_p} \P[\widehat{S}_p\neq S_p] = 1,
\end{align*}
when $\overline{r}<g(\beta)$, where the last line follows from Theorem \ref{thm:necessary}.
\end{proof}

@@

Theorem \ref{thm:necessary-strengthened} and Corollary \ref{cor:minimax-over-dependence} provide a nearly complete picture of the difficulty 
in the exact support  recovery problem, in the regime when the thresholding estimators are optimal. Specifically, in such cases the signal classification boundary is universal.  On the other hand, Theorem \ref{thm:likelihood-ratio-thresholding}, and indeed, Example \ref{exmp:suboptimal-data-thresholding} demonstrate that thresholding procedures are \emph{sub-optimal} for $\text{AGG}(\nu)$ models with $\nu<1$. Therefore, the optimality of thresholding
procedures (specifically, Bonferroni's procedure) only applies to $\text{AGG}(\nu)$ models with $\nu\ge1$. 
% This suggests that the condition $\nu\ge1$ in Corollary \ref{cor:minimax-over-dependence} is tight.
